\documentclass[fullpage,10pt, onecolumn, draftclsnofoot]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage[margin=.75in]{geometry}
\usepackage{setspace}
\singlespacing

\title{CS60 Patient Safety App: A Volume-based Enteral Feeding Calculator}
\author{Alison Jones\\ CS461 - Senior Project \\Fall 2019}

\begin{document}
\pagenumbering{arabic}
\maketitle


\section{Introduction}

\subsection{Purpose}
The volume-based enteral feeding calculator replaces the paper tables currently used when 
calculating feed rates for both gastric and small bowel enteral feeding. The calculator reduces
error by requiring the source numbers to be entered and automatically produced, unlike the current
method which requires the result to be produced by hand. The goal of this conversion is to reduce both
error and time taken in getting the results.

\subsection{Background}
Paper tables have been designed for nurses to use to calculate the catch up rate. The table is a commonly used rate-based system with a max rate cap based on the method of feeding. Many hospitals don't even use this method and just had calculate the catchup rate. The current method leaves some room for error and could be improved/automated.

\subsection{References}
(TBD)

\section{Overall Description}
\subsection{Product Overview}
The application and its source code will be released on GitHub. Both the compiled binary and the source code
will be appropriately licensed for its own open source distribution and to be license compatible with any 
libraries, code, or other intellectual property used to create the application.

The platform for the project will be determined from surveying nurses to determine whether mobile or desktop
is more convenient and widespread for projects of similar scale and niche.

\subsection{Product Functions}
This product is meant to calculate volumetric feeding rate. The final function of it should be to make nurse's jobs easier when dealing with enteral feeding calculations. The application should be user friendly and easy to learn. It should require no math for nurses to complete their initial task. The product will be open source and available for all.

\subsection{System Interfaces}
The enteral feeding calculator will interface with local storage on the machine to store any generated 
error logs and to save values which are not likely to change after being first set. The calculator will
also display to the user's screen and input devices via a UI library to interface with the operating system's screen drawing
routines and to accept pointer and text input from the user.

\subsection{User Interfaces}
The user interface will be minimal and easy to read. The application will have no configuration window
or views other than its main interface, and on its main interface will have the text inputs for the different
input values: time of feeding stop, time of feeding restart, reset time of feeding, and daily feeding volume.

Time inputs will allow only numerical values, a colon, and optionally AM/PM inputs. Any time with a PM will
have 12 added to its value automatically before being used for calculations. A time with PM at the end cannot have an hour value greater than 12.
Volume inputs will accept only numerical values. A checkbox will be used to indicate whether the feeding type is gastric or
small bowel, with a large banner indicating the current state. At the bottom of the UI will be the output value and a calculation
button that updates the output value, if valid.

\section{Specific Requirements}

\subsection{Functions}
The project must have the following functions upon completion. The application must do the required math/logic and it must be done correctly. The app should be able to get date and time information for these calculations. As the user enters and updates information, it should be updated where applicable. Variables that should eb constant should be locally saved when se so that they aren't changed.

\subsection{Software Quality}
The enteral feeding calculator will need to have support for multiple versions of its target platform. Medical settings often
have a variety of versions for device operating systems. If the mobile platform is chosen, the software will need to support 
multiple versions of both the Android and iOS mobile operating systems. If the desktop platform is chosen, the software will need
to support legacy and current versions of Windows, from Windows 7 to Windows 10.

The software should not crash, freeze, or return erroneous results over normal use. The results returned by the program should never
exceed the maximum safe values for their kind of enteral feeding, even with erroneous input. Results should also be consistent over
up time of the application and regardless of the uptime of the operating system.

The user interface should indicate when a value is accepted or rejected, and offer further clarity through its interface with minimal clutter.

\section{Verification}
After being proven to work, the final project will hopefully make it into clinical testing. This is the true test to verify how effective the project is. The application should ultimately be well received and have a lowered chance for error. We can test this by comparing the percent error before and after implementation.

\end{document}
